---
title: "Historical horse population in Canada"
bibliography: horse_refs.bib
params:
  province: "Alberta"
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(tidyverse)
```

## Aim

This project explores the historical population of horses in Canada between 1906 and 1972 for each Province.


## Data

```{r load data, include = FALSE}
horse_pop <- read_csv("../data/00030067-eng.csv")
horse_pop <- filter(horse_pop,
                    DATE == "At June 1 (x 1,000)",
                    GEO != "Canada")
horse_pop$Value <- horse_pop$Value * 1000
```

Horse population data were sourced from the [Government of Canada's Open Data website](http://open.canada.ca/en/open-data). Specifically, these two sources were used:

- [Horses, number on farms at June 1 and at December 1](http://open.canada.ca/data/en/dataset/43b3a9b3-3842-45e7-8bc8-c4c27b9462ab)
- [Horses, number on farms at June 1, farm value per head and total farm value](http://open.canada.ca/data/en/dataset/b374f60b-9580-44dc-83f6-c0a850c15f30)

## Methods

The R programming language [@R] and the following R packages were used to perform the analysis: knitr [@knitr] and tidyverse [@tidyverse]. The code used to perform the analysis and create this report can be found here: https://github.com/ttimbers/equine_numbers_value_canada_rmd.

